A weakly structured stem for human origins in Africa

### 2022-03-04 paper.tex
tiny cleanup discussion'

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb}. The fossil
record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar to present-day humans (e.g., from Omo
Kibish, Ethiopia), others are similar in some features but not others (e.g.,
from Jebel Irhoud, Morocco), and others are very different (e.g., from
Dinaledi, South Africa) in morphology. If, as our model predicts, the
morphological differences between the stems were comparable to those among
present-day human populations, the most divergent fossils are unlikely to
represent the branches that contributed appreciably to present-day human
ancestries.

>>>>

Multiple studies have shown a correspondence between phenotypic
differentiation, usually assessed with measurements of the cranium, and genetic
differentiation among human populations and between humans and Neanderthals
\citep{Relethford1994-mh,Weaver2008-ho,Von_Cramon-Taubadel2009-zb} (see also Section \ref{morpho_diff}). The fossil
record of Africa is sparse during the time period of the stems, but of the
available fossils, some are very similar to present-day humans (e.g., from Omo
Kibish, Ethiopia), others are similar in some features but not others (e.g.,
from Jebel Irhoud, Morocco), and others are very different (e.g., from
Dinaledi, South Africa) in morphology. If, as our model predicts, the
morphological differences between the stems were comparable to those among
present-day human populations, the most divergent fossils are unlikely to
represent branches that contributed appreciably to present-day human
ancestries.
